---
title: "Google Summer of Code Contributions"
author: "Lorenz Walthert"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Google Summer of Code Contributions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vigette aims to summarize the contributions made to styler through 
Google Summer of Code 2017.

# High-level overview
The author 

* opened over [60](https://github.com/krlmlr/styler/issues?utf8=✓&q=is%3Aopen%20is%3Aissue%20author%3Alorenzwalthert%20created%3A%3C2017-08-31%20%20created%3A%3E2017-06-01%20) issues and closed the majority of them with his own pull requests.
* created more than [60](https://github.com/krlmlr/styler/pulls?q=is%3Apr+author%3Alorenzwalthert+created%3A%3C2017-08-31++created%3A%3E2017-06-01) pull requests to
  master of which the vast majority was merged.

The activity during GSOC can be grouped into the following steps:

* Replicating the outcomes that were achieved with flat styling with nested 
  styling. Required implementeation of the visitor as well as different 
  serialization method.
* Adding functionality that was only possible with the nested styling such 
  as indention based on operators (`+`, `%>%` etc.), braces `{` and `(`. 
  the use of raw indention, allowing for token-dependent re-indention.
* Infrastructure changes such as serialized testing, improve performance, 
  create mutli-line attribute, code refactoring. Partially
  flattening out the nested parse table.
* Extending the functionality that was not there with the flat approach. 
  Examples include styling multiple expressions, token replacement (e.g. `<-` for 
  `=`), line break rules (invasive and non-invaive), token insertion (`()` in 
  function calls within pipes), RStudio Addins, styling of comments, styling of 
  a single file, public api redesign, spacing around more operators (colons, 
  commas, infix operators, bang-bang).

The list above is not comprehensive and covers only the large contributions.
Always along with coding, documentation and tests were provided.

# Low-level analysis

We can use the package `gitsum` to perform an analysis of the GitHub repository.
```{r, message = FALSE}
library("gitsum")
library("tidyverse")
log <- git_log_detailed() %>%
  filter(date > as.Date("2017-06-01"), date < as.Date("2017-08-31"))
```

We can see that the vast majority of the commits in this period comes from the 
student and a few from the main mentor.
```{r}
log %>%
  group_by(author_name) %>%
  count()
```


We can also look at how the number of lines in the different files eveolved
```{r}
lines <- log %>%
  add_line_history()

r_files <- grep("^R/", lines$changed_file, value = TRUE)

to_plot <- lines %>%
  filter(changed_file %in% r_files) %>%
  group_by(changed_file) %>%
  mutate(has_changed = n() > 1) %>%
  filter(has_changed)
  
ggplot(to_plot, aes(x = date, y = current_lines)) + 
  geom_step() + 
  scale_y_continuous(name = "Number of Lines", limits = c(0, NA)) + 
  facet_wrap(~changed_file, scales = "free_y")
```

The total number of insertions and deletions by the author is
```{r}
log %>%
  filter(author_name == "Lorenz Walthert") %>%
  summarize(sum(total_insertions) + sum(total_deletions)) %>%
  pull()
```

Which still contains many insertions and deletions in some files that were
generated as a biproduct, so let's focus on the code in the `R` directory.

```{r}
log %>%
  unnest() %>%
  filter(dirname(changed_file) == "R") %>%
  summarize(sum(insertions) + sum(deletions)) %>%
  pull()
```

